A Data-Driven Early Warning System for Mining Accident

### 2017-03-21 San Antonio/slides/presentation_slides.Rmd
updated slides

- Link: <https://enforcedata.dol.gov/views/data_catalogs.php>
- Updated daily or weekly
- Enforecement Data Catalog
    - MSHA Enforcement Data
    - OSHA Enforcement Data
    - Wage and Hour Compliance Action Data
    - OFCCP Compliance Evaluation and Complaint Investigation Data
    - EBSA Enforcement Data

@@

- Missing data
- Inactive mines
- Most data are not numeric
- Relatively few severe accidents ($\sim0.5\%$)

## Model Preliminaries

- Create a master data table with selected attributes
- Plot violation trends for Upper Big Branch Mine and Sago Mine
- Design a predictive model

## Master Data Table

@@

## Master Data Table

@@

- Biostatisticians and epidemiologists call it "conditional logistic regression" (`survival::clogit`)
- Suitable for panel data (e.g., our master data table)
- Model includes mine-specific but time-invariant variables (e.g., same slope but different intercepts for different mines)
- Logistic regression (for every mine)

@@

- Train and test on all data

@@

- True positives

@@

- Top predicted positives (possibly false positives)

@@

- Randomly select half of the data to train and the other half to test

@@

- Top true positives (deadliest accidents)

@@

- Top predicted positives (possibly false positives)

@@

<!--- Violation trend prior to the first quarter in 2006 where model probability is 0.99-->

@@

- Top true positives (deadliest accidents)

@@

- Top predicted positives (possibly false positives)

@@

@@

<!-- - Causal relationship between accidents and historical data -->
- Summary
    - Two deadliest mine accidents in the last decade: Upper Big Branch & Sago
    - MSHA

>>>>

- Link: <https://enforcedata.dol.gov/views/data_catalogs.php>
- Updated daily or weekly
- Enforecement Data Catalog
    - MSHA Enforcement Data
    - OSHA Enforcement Data
    <!-- - Wage and Hour Compliance Action Data -->
    <!-- - OFCCP Compliance Evaluation and Complaint Investigation Data -->
    <!-- - EBSA Enforcement Data -->
    <!-- - Department of Justice -->
    - EPA
    - FDA

@@

- Missing data, typos
- Inactive mines are not labeled
- Most data are not numeric
- Relatively few severe accidents ($\sim0.5\%$)

<!-- ## Model Preliminaries -->

<!-- - Create a master data table with selected attributes -->
<!-- - Plot violation trends for Upper Big Branch Mine and Sago Mine -->
<!-- - Conduct statistical analyses -->

## Consolidated Data

@@

## Consolidated Data

- Number of days lost (`num.days.lost`), numer of days restricted (`num.days.restrict`), number of deaths (`num.death`), number of permenant disabilities (`num.dis`), and number of violations (`viol.quantity`)

@@

- Biostatisticians and epidemiologists call it "conditional logistic regression" (`survival::clogit`)
- Suitable for **panel data** (e.g., our consolidated data)
- Model includes mine-specific but time-invariant variables
- Logistic regression (for every mine)

@@

<!-- 解释 confusion matrix和 specificity -->

- In-sample model

@@

- Fail to predict top 10 true positives

@@

- False positive predictions
<!-- - Top predicted positives (possibly false positives) -->

@@

- Out-of-sample model (randomly select half of the data to train and the other half to test)

@@

- Successfully predict all top 10 true positives

@@

- False positive predictions

@@

<!--- Violation trend prior to the first quarter in 2006 where model probability is 0.99-->
<!-- 即便没有灾难，也有趋势，警示作用，后来可能改善了 -->

@@

- Successfully predict 9 out of top 10 true positives

@@

-

@@

## Unsupervised Clustering

## Markov Chain

@@

<!-- - Causal relationship between accidents and historical data -->
- Summary
    - Two deadliest mine accidents in the last decade: Upper Big Branch & Sago
    - MSHA 
- Application
    - "Credit score" for mine safety
    - Regulators, mines, stakeholders
- Future
    - Expand data: OSHA, EPA, etc.
    - Models and techniques: artificial neural networks (restricted boltzmann machine), text mining, etc.
